---
title: "Reading Reddit Comments"
author: "Rasmus Holm"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

This package supports two types of read operations on Reddit comments. \code{read_reddit_raw} and \code{read_reddit_stream} that are suited for small respectively large files. It is important to know that they assume different structure in the file. The raw-mode expects typical json-format where all json-objects are enclosed in '[]' and separated by ','. The stream-mode on the otherhand expect that each row contains a json-object, thus separation is '\\n'.

# Reading using raw

```{r}
suppressMessages(library(reddy))
suppressMessages(library(dplyr))

filename <- paste(system.file("extdata", package="reddy"),
                  "RC_2008_01_1000_raw.json", sep="/")
corpus_raw <- read_reddit_raw(filename) %>%
    remove_attrs(c("id", "body"), negative=TRUE)
head(corpus_raw)
```

# Reading using stream

```{r}
filename <- paste(system.file("extdata", package="reddy"),
                  "RC_2008_01_1000_stream.json", sep="/")
corpus_stream <- read_reddit_stream(filename) %>%
    remove_attrs(c("id", "body"), negative=TRUE)
head(corpus_stream)
```
